\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A Guide for International Students

### 2023-10-26 demystify.tex
Updates from Overleaf

This section lists various issues that international students should pay attention to.

@@

\paragraph{Illegal Software} Using illegal/cracked software is very common in many countries (and even in the US). However, \emph{do not} install or use them on university computers (e.g., those given by your department or advisor).  It is unlikely that the university will track you down, but it is the \emph{software company} that will.  They have very sophisticated tools to detect illegal software and will sue your university/department.  Imagine your department or advisor being sued for half a million dollars, and it is \emph{you} who caused it.  If you need software, ask your advisor or the department.

>>>>

This section lists various cultural issues that international students should pay attention to.

@@

\paragraph{Illegal Software} Using illegal/cracked software is very common in many countries (and even in the US). However, \emph{do not} install or use them on university computers (e.g., those given by your department or advisor).  It is unlikely that the university will track you down, but it is the \emph{software company} that will.  They have very sophisticated tools to detect illegal software and will sue your university/department.  Imagine your department or advisor being sued for a large sum of money, and it is \emph{you} who caused it.  If you need software, ask your advisor or the department.
